\documentclass[10pt]{article}

\usepackage{fullpage}

\title{COS 516: Class Project Outline\\
\emph{Project Name}}

\author{\emph{Student1 Name, Student2 Name}} 

\begin{document}
\maketitle

\section{Introduction}

Describe in a few sentences WHAT problem you will be addressing. Feel free to use the text in the list of projects as a starting point, but make it specific to the scope of your project.

\section{Proposed Work}

Describe briefly HOW you will be solving the problem. Provide as many relevant details as you can about the following items (not all of these might apply to your project). 
\begin{itemize}
\item which tool(s) you plan to use
\item which examples you plan to target
\item what modules you plan to create or implement
\item what experiments you will conduct
\item what deliverables you will provide (in addition to a final project report) \\
For example, this could include working examples, working code, scripts for running tests/experiments, result output from tools, etc.
\item any other relevant aspects
\end{itemize}
It is fine if you change these as you make progress in the project. 

\section{Proposed Schedule}

Describe briefly WHEN you plan to do what. This is to help you plan out chunks of work you will need to do for the project.  
Keep in mind the following important dates:
\begin{itemize}
\item project presentations: November 25, December 2 and 4 (in class, schedule is TBD).
\item final project report: due on December 13.
\end{itemize}

\end{document}
